%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Om Kumar} \\ \vspace{1pt}
    \small +91 7827498703 $|$ \href{mailto:x@x.c}{\underline{omkumar742003@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/om-kumar-100om/}{\underline{linkedin.com/in/om-kumar-100om}}
    $|$
    \href{https://github.com/Omkumar2003}{\underline{github.com/Omkumar2003}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{New Delhi}
      {Bachelor of Computer Applications}{2021 -- 2024}
    \resumeSubheading
      {Guru Gobind Singh Indraprastha University}{New Delhi}
      {Master of Computer Applications}{2024 -- 2026}
    % \resumeSubheading
    %   {New Green Field School}{Alaknanda, New Delhi}
    %   {Class XII}{2021}
    % \resumeSubheading
    %   {New Green Field School}{Alaknanda, New Delhi}
    %   {Class X}{2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
% \section{Experience}
%   \resumeSubHeadingListStart

%     \resumeSubheading
%       {Web Development Intern}{June 2024 -present}
%       {Prodigy InfoTech}{}
%       \resumeItemListStart
%         \resumeItem{As part of my role at Prodigy InfoTech, I took the initiative to create a personal profile website to showcase my skills, projects, and professional experience. }
%         \resumeItem{ Utilized React's component-based architecture, Tailwind's utility-first CSS framework, and Node.js for server-side logic. }
%       \resumeItemListEnd
      
% % -----------Multiple Positions Heading-----------
% %    \resumeSubSubheading
% %     {Software Engineer I}{Oct 2014 - Sep 2016}
% %     \resumeItemListStart
% %        \resumeItem{Apache Beam}
% %          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
% %     \resumeItemListEnd
% %    \resumeSubHeadingListEnd
% %-------------------------------------------

%     \resumeSubheading
%       {Java developer Intern}{June 2024 -- Present}
%       {CodeAlpha}{}
%       \resumeItemListStart
%         \resumeItem{I had the opportunity to delve into the fundamentals of Java programming language and gain a deeper understanding of its core concepts.}
%         \resumeItem{Through hands-on experience and guided learning sessions, I explored topics such as object-oriented programming (OOP), data types, control flow, and exception handling in Java.}
       
%     \resumeItemListEnd




%   \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MINDMAP WEBSITE} $|$ \emph{React, Express js, Node js, Mongo DB, Redux toolkit, Tailwind}}{}
          \resumeItemListStart
            \resumeItem{Led the end-to-end development of a sophisticated mind mapping website using the MERN stack (MongoDB, Express.js, React, Node.js) and Tailwind CSS for the user interface.}
            \resumeItem{Engineered a robust mind mapping application designed to facilitate the visualization and simplification of complex theories. Enhanced user comprehension and retention rates by 40\% in educational settings through interactive diagrams and visual aids.}
            \resumeItem{Mastered advanced React features such as Hooks and Context API, coupled with Tailwind CSS, to create a highly responsive and aesthetically pleasing user interface. Implemented state management using Redux Toolkit for efficient data handling and application scalability.}
            \resumeItem{Developed and integrated over 5 customizable templates, allowing users to personalize their mind maps extensively, thus improving user engagement and satisfaction.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{INTERPRETER IN GO} $|$ \emph{Golang, Git}}{}
          \resumeItemListStart
            \resumeItem{Designed and implemented a Go-based interpreter for the Monkey programming language, utilizing a Pratt parser to handle complex parsing requirements.}
            \resumeItem{Gained deep expertise in compiler design, including concepts such as deterministic finite automata (DFA), types parsing, token generation, syntax and grammar analysis, and automata theory. Applied these principles to build a robust interpreter.}
            \resumeItem{Enhanced the interpreter’s functionality by integrating a Read-Eval-Print Loop (REPL) for interactive code execution and file processing capabilities for batch execution, significantly increasing the tool's versatility and user applicability.}
            \resumeItem{Optimized memory usage by 10\% through targeted memory management techniques and performance enhancements, leading to more efficient execution and reduced resource consumption.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MICROBALANCER} $|$ \emph{Java}}{}
          \resumeItemListStart
            \resumeItem{Developed a sophisticated load balancer for microservices architecture using Java, implementing both round-robin and weighted round-robin strategies to effectively distribute incoming traffic across multiple service instances.}
            \resumeItem{Designed and implemented configuration management through YAML files, allowing dynamic specification and management of service replicas' locations. This approach facilitated flexible and scalable deployment configurations.}
            \resumeItem{Enhanced system reliability and load distribution by applying advanced load balancing algorithms and optimization techniques, resulting in improved application performance and reduced latency. Implemented comprehensive monitoring and logging features for real-time performance tracking and troubleshooting.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C\#, SQL JavaScript, HTML/CSS, Golang} \\
     \textbf{Frameworks}{:Express js, React js , Node js, .Net, J2EE} \\
     \textbf{Developer Tools}{: Git, GitHub, VS Code, Jupyter Lab, IntelliJ, Postman, Visual Code, Docker} \\
     % \textbf{Libraries}{: pandas,  }\\
     % \textbf{Data Analytics}{:Data preparation, Machine Learning, Deep Learning }\\
     \textbf{Others}{: Redux , Tailwind , Hibernate}
     % \textbf{Other}{: Erp, ABAP}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
